\vspace{-1.5em} \bf A general and efficient representation of ancestral recombination graphs

### 2024-04-04 paper.tex
WIP

Note that the \citet{wiuf1999recombination} eARG
in Fig.~\ref{fig-ancestry-resolution} is not particularly
representative, because inference or simulation methods usually
only generate ARGs containing nodes and edges ancestral to the sample
(but see the discussion of the ``Big ARG'' stochastic process in
Appendix~\ref{sec-big-and-little-arg}).
Nonetheless, it is an instructive example from the literature which highlights several
important properties of ARGs, and the general point about
the need to resolve ancestral material ``on the fly'' for eARG traversals
holds.

\section{A diversity of structures}

There are a number of tools for inferring genetic genealogies,
and the graph structures that they produce differ in important aspects.
These varying representations have all been termed ``ARGs'' by different authors,
and each describes more than a simple sequence of uncorrelated trees.
By way of illustration, Fig.~\ref{fig-inferred-args} depicts the output of four
different ``ARG inference'' tools run on a common dataset,
with the resulting ARGs converted into a standard gARG format (cite tskit).

@@

>>>>

% Note that the \citet{wiuf1999recombination} eARG
% in Fig.~\ref{fig-ancestry-resolution} is not particularly
% representative, because inference or simulation methods usually
% only generate ARGs containing nodes and edges ancestral to the sample
% (but see the discussion of the ``Big ARG'' stochastic process in
% Appendix~\ref{sec-big-and-little-arg}).
% Nonetheless, it is an instructive example from the literature which highlights several
% important properties of ARGs, and the general point about
% the need to resolve ancestral material ``on the fly'' for eARG traversals
% holds.

\section{A diversity of structures}
A key goal of this perspective is to highlight the heterogeneity of
the graph structures inferred by modern ARG inference methods.
To illustrate this point, Fig.~\ref{fig-inferred-args} shows the 
output of four methods run on the 
\cite{kreitman1983nucleotide} dataset, often used as an
ARG inference benchmark. One source of differences between 
the inferences is the underlying model. For instance, 
the ARG in Fig.~\ref{fig-inferred-args}A is inferred by 
\kwarg\ under parsimony, and therefore has many fewer 
ancestral nodes then Fig.~\ref{fig-inferred-args}B, which 
is sampled from the coalescent with recombination with an 
appropriate recombination rate parameter. These differences
are well understood.

@@

The differences between ARGs that we wish to draw attention to here 
are more subtle
